STR: Seasonal-Trend decomposition using Regression

### 2020-11-17 str_ijds.Rmd
Reverted to original ordering of authors

---
title: "STR: Seasonal-Trend decomposition using Regression"
author:
 - familyname: Hyndman
   othernames: Rob J
   address: Monash University\newline Australia
   email: Rob.Hyndman@monash.edu
   correspondingauthor: true
 - familyname: Dokumentov
   othernames: Alexander
   address: Growing Data\newline Australia
abstract: "We propose a new method for decomposing seasonal data: STR (a Seasonal-Trend decomposition using Regression). Unlike other decomposition methods, STR allows for multiple seasonal and cyclic components, covariates, seasonal patterns that may have non-integer periods, and seasonality with complex topology. It can be used for time series with any regular time index including hourly, daily, weekly, monthly or quarterly data. It is competitive with existing methods when they exist, but tackles many more decomposition problem than other methods allow.\\par STR is based on a regularized optimization, and so is somewhat related to ridge regression. Because it is based on a statistical model, we can easily compute confidence intervals for components, something that is not possible with most existing decomposition methods (such as STL, X-12-ARIMA, SEATS-TRAMO, etc.).\\par
  Our model is implemented in the R package *stR*, so can be applied by anyone  to their own data."
keywords: "time series decomposition, seasonal data, Tikhonov regularisation, ridge regression, LASSO, STL, TBATS, X-12-ARIMA, BSM"
blind: false
cover: false
toc: false
bibliography: strrefs.bib
biblio-style: authoryear-comp
output:
  MonashEBSTemplates::workingpaper:
    fig_caption: yes
    fig_height: 5
    fig_width: 8
    toc: no
    keep_tex: yes
    number_sections: yes
    citation_package: biblatex
header-includes:
  - \graphicspath{{figs/}}
  - \def\addlinespace{}
  - \usepackage{amsmath}
  - \setlength{\arraycolsep}{3pt}
  - \setcounter{MaxMatrixCols}{20}
  - \newcommand{\argmin}{\operatorname{arg\,min}}
  - \newcommand{\sn}{\kappa}
  - \renewcommand{\vec}{\operatorname{vec}}
  - \newcommand{\diag}{\operatorname{diag}}
  - \renewcommand{\mod}{\operatorname{mod}}
  - \usepackage[section]{placeins}
---

>>>>

---
title: "STR: Seasonal-Trend decomposition using Regression"
author:
 - familyname: Dokumentov
   othernames: Alexander
   address: Growing Data\newline Australia
 - familyname: Hyndman
   othernames: Rob J
   address: Monash University\newline Australia
   email: Rob.Hyndman@monash.edu
   correspondingauthor: true
abstract: "We propose a new method for decomposing seasonal data: STR (a Seasonal-Trend decomposition using Regression). Unlike other decomposition methods, STR allows for multiple seasonal and cyclic components, covariates, seasonal patterns that may have non-integer periods, and seasonality with complex topology. It can be used for time series with any regular time index including hourly, daily, weekly, monthly or quarterly data. It is competitive with existing methods when they exist, but tackles many more decomposition problem than other methods allow.\\par STR is based on a regularized optimization, and so is somewhat related to ridge regression. Because it is based on a statistical model, we can easily compute confidence intervals for components, something that is not possible with most existing decomposition methods (such as STL, X-12-ARIMA, SEATS-TRAMO, etc.).\\par
  Our model is implemented in the R package *stR*, so can be applied by anyone  to their own data."
keywords: "time series decomposition, seasonal data, Tikhonov regularisation, ridge regression, LASSO, STL, TBATS, X-12-ARIMA, BSM"
blind: false
cover: false
toc: false
bibliography: strrefs.bib
biblio-style: authoryear-comp
output:
  MonashEBSTemplates::workingpaper:
    fig_caption: yes
    fig_height: 5
    fig_width: 8
    toc: no
    keep_tex: yes
    number_sections: yes
    citation_package: biblatex
header-includes:
  - \graphicspath{{figs/}}
  - \def\addlinespace{}
  - \usepackage{amsmath}
  - \setlength{\arraycolsep}{3pt}
  - \setcounter{MaxMatrixCols}{20}
  - \newcommand{\argmin}{\operatorname{arg\,min}}
  - \newcommand{\sn}{\kappa}
  - \renewcommand{\vec}{\operatorname{vec}}
  - \newcommand{\diag}{\operatorname{diag}}
  - \renewcommand{\mod}{\operatorname{mod}}
  - \usepackage[section]{placeins}
---
